---
title: "Per-36 Stat and Percentile in the NBA"
author: "Terry Wang"
date: "9/7/2017"
output: ioslides_presentation
---

## Executive summary
- This app allows users to input values for a boxscore stat (points, rebounds, and assists) and returns the values' percentiles during the
 '13-'14 NBA season, as well as the player with the most similar stat value as the input
- In the NBA, using per-36 minute stats can adjust for playing time and better reflect a player's statistical contribution to a team when
he is on the court
- This tool helps users to get a sense of the per-36 stats
- It might also allow people find underappreciated players in the NBA

## How the app works
The app requires an csv file containing the aggregated boxscore stats from the '13-'14 nba season.
From the UI, users input the desired stat and an value for that stat.  
For example, if an user wants to check the percentile of 10 points per 36-minutes, he/she can simply use the dropdown menu to select "Points" and type in the input box the number 10.
The app graps the column in the dataset that corresponds to the input stat, calculates per-36 minute value for that stat using another column that indicates total minutes played, finds the distribution of the per-36 stat, and returns the percentile of the user's input value.
The app then finds the player with the most similar stat by finding which row corresponds to the lowest absolute value of the user's input minus the per-36 values in the dataset.

## Code demonstration

To check the percentile of 10 points per 36 minutes during the '13-'14 NBA season:
```{r}
nba2013 <- read.csv("nba_2013.csv")
stat <- as.character("pts")
name <- nba2013$player
stat.36 <- nba2013[, grep(stat, names(nba2013))]/(nba2013$mp/36)
x36 <- data.frame("name" = name, "stat.36" = stat.36)
pct <- ecdf(x36$stat.36)
pctile <- round(pct(10)*100, 1)
print(paste(pctile, "th Percentile"))
```

## Code demonstration

To check the player with points per 36 minutes that is the closest to 10:
```{r}
stat <- as.character("pts")
name <- nba2013$player
stat.36 <- nba2013[, grep(stat, names(nba2013))]/(nba2013$mp/36)
x36 <- data.frame("name" = name, "stat.36" = stat.36)
simplyr <- x36[which.min(abs(10-x36$stat.36)),]
print(paste(simplyr$name, "-", round(simplyr$stat.36,1)))
```


